The eclipse of ASASSN-21qj

### 2022-11-10 src/tex/ms.tex
[showyourwork] overleaf sync

To search for signs of periodicity within the light curve before and during the eclipse, we perform a Lomb-Scargle analysis over two epochs indicated with the blue and orange regions in the upper panel of Figure\~\ref{fig:starlombscargle}.
%
The resultant periodograms are shown in the lower two panels of Figure\~\ref{fig:starlombscargle}, with the lower panel showing a zoom in from 0 to 50 days and the middle panel showing periodicities from 0 to 150 days.
%
We look for any perioditicies that could be associated with orbital motion aorund the star, so we look at the periodogram from 0 to 150 days during the eclipse.
%
As a comparison, we overplot the periodogram for the pre-eclipse light curve as the blue curve in the middle panel. 
%
As can be seen, there is some power seen at 40 days which is present in the pre-eclipse light curve, with some (non-significant) periodicities at longer periods.

>>>>

%To search for signs of periodicity within the light curve before and during the eclipse, we perform a Lomb-Scargle analysis over two epochs indicated with the blue and orange regions in the upper panel of Figure\~\ref{fig:starlombscargle}.
%
%The resultant periodograms are shown in the lower two panels of Figure\~\ref{fig:starlombscargle}, with the lower panel showing a zoom in from 0 to 50 days and the middle panel showing periodicities from 0 to 150 days.
%
We look for any perioditicies that could be associated with orbital motion aorund the star, so we look at the periodogram from 0 to 150 days during the eclipse.
%
As a comparison, we overplot the periodogram for the pre-eclipse light curve as the blue curve in the middle panel. 
%
As can be seen, there is some power seen at 40 days which is present in the pre-eclipse light curve, with some (non-significant) periodicities at longer periods.
